---
name: Michael
surname: Schramm
address: "3406 Judythe Ct. Bryan, TX 77803"
phone: 910 232 3760
www: michaelpaulschramm.com
email: "mpschramm@gmail.com"
twitter: mpschramm
github: mps9506
date: "`r format(Sys.time(), '%B %Y')`"
docname: Resume
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(RefManageR)
library(vitae)
```

\setbool{acvSectionColorHighlight}{false}

As a research professional providing expertise in water science, policy, and regulation, I leverage statistical and geospatial analysis to bridge the gaps between science and stakeholders. I invest my time in developing open source data tools and methods to ensure transparency and reproduciblity in the work I communicate to the public. Since 2016, I have authored nine papers or reports on water resources topics. 

# Skills

**Communication:** academic writing, extension and outreach programs, stakeholder facilitation, technical and non-technical reports

**Programatic:** grant writing, project management, proposal development

**Programming and Applications:** ArcGIS, Excel, git (limited), `R`, `Python`

**Water Management and Hydrologic Science:** statistical methods for water quality, TMDL development, water quality policy and regulations, watershed planning

# Employment

```{r Experience}
library(tibble)
tribble(
  ~Year, ~Company, ~Title, ~Description, ~Location,
  "2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Specialist III", "Collaborate with researchers to design, plan, conduct, and coordinate water focused research projects.", "College Station, TX",
    "2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Specialist III", "Facilitate stakeholder engagement to inform research priorities that address local research needs.", "College Station, TX",
      "2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Specialist III", "Supervise undergraduate and/or graduate students and other technical or field staff involved in research.", "College Station, TX",
        "2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Specialist III", "Represent TWRI at local, national, and international meetings to disseminate research findings and network with peers in the field.", "College Station, TX",
          "2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Specialist III", "Prepare and write proposals to funding agencies; maintain financial accounts related to research projects.", "College Station, TX",
  "2016 - 2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Associate", "Provide technical support and stakeholder facilitation of watershed planning, TMDL, and I-Plan projects in collaboration with state water resource agencies.", "College Station, TX",
    "2016 - 2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Associate", "Develop, evaluate, and apply research and statistical methods for water resources planning.", "College Station, TX",
      "2016 - 2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Associate", "Collborated with state agencies and local stakeholders to publish watershed protection plans, TMDLs, Implementation Plans, and technical reports assessing indicator bacteria pollutant loads.", "College Station, TX",
        "2016 - 2019", "Texas Water Resources Institute, Texas A&M AgriLife Research", "Research Associate", "Worked with Institute scientists and other entities to secure seven projects and $1.3 million in research and water quality improvement funding.", "College Station, TX",
  "2014-2016", "Oak Ridge National Laboratory/Oak Ridge Associated Universities", "Research Associate", "Develop relational database and methods to assess environmental mitigation at U.S. hydropower facilities.", "Oak Ridge, TN",
    "2014-2016", "Oak Ridge National Laboratory/Oak Ridge Associated Universities", "Research Associate", "Utilize statistical and geospatial methods to analyze data.", "Oak Ridge, TN",
      "2014-2016", "Oak Ridge National Laboratory/Oak Ridge Associated Universities", "Research Associate", "Published three peer-reviewed journal articles, two technical reports, and one conference presentation on research findings related to mitigating environmental impacts of hydropower facilites.", "Oak Ridge, TN",
  "2013-2014", "Center for Energy and Environmental Policy, University of Delaware", "Graduate Research Assistant", "Responsible for interviews, data analysis, and developing policy reccomendations in two policy analysis reports delived to the state General Assembly.", "Newark, DE"
) %>% 
  detailed_entries(
    what = Title,
    when = Year, 
    with = Company,
    where = Location,
    why = Description
  )
```

# Education

```{r Education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "B.S. Biology", "2004", "University of North Carolina - Wilmington", "Wilmington, NC",
  "B.A. Environmental Studies", "2011", "University of North Carolina - Wilmington", "Wilmington, NC",
  "Master of Energy and Environmental Policy", "2013", "University of Delaware", "Newark, DE"
) %>%
  arrange(desc(Year)) %>%
  detailed_entries(Degree, Year, Institution, Where)
```


# Selected Publications

```{r Publications}
# Not sure how to get special charcters escaped in the output bib file.
# scholar::get_publications("a7KtAHMAAAAJ") %>%
#   filter(cites >= 10) %>%
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>%
#   mutate(journaltitle = gsub("&","\\&",journaltitle)) %>%  ## Fix & in title
#   RefManageR::as.BibEntry() %>%
#   RefManageR::WriteBib("schramm.bib")

bibliography_entries("schramm_pubs.bib") %>%
  filter(bibtype == "Article") %>%
  arrange(date)
```


# Software (R)

```{r Rbib, include=FALSE}
# Construct bib file for R packages
source("Rpackages.R")
write_packages_bib(
  pkglist = c("echor","tbrf","dartx"),
  file="Rpackages.bib")
```

```{r Rpackages}

# Sort R packages by title, then year.
bibliography_entries("Rpackages.bib",
  startlabel = "packagestart", endlabel = "packageend"
) %>%
  arrange(title, year)
```
